Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-14 ieee_paper.tex
format

Each core in the architecture has a 32kB L1 data cache, a 32kB L1
instruction cache, and a 512kB L2 cache. The architecture of a core is
based the traditional Pentium architecture which have been extended to
64-bit. A core can hold 4 hardware contexts at any time. And at each
clock cycle, instructions from a single thread are executed. Due to
some hardware constraints two hardware context must be used to reach
the peak instruction throughput in that architecture. As in the
Pentium architecture, a core has two different concurrent instruction
pipelines which allow the execution of two instructions per
cycle. However, only one vector or floating point instruction can be
executed at each cycle.

@@

\todo{rewrite that to make sure it fits the description of the card
  used in the experiments. This text with copy/pasted from the PPAM
  paper}

@@

\section{Conclusion}
\label{sec:ccl}
In the previous sections, we have explored in the practical implementation on a MIC architecture of multiple derivative operators acting on multiple vectors within the context of RBF-RD. Each derivative has an associated sparse matrix with a fixed number
of non-zeros on each row. While computing a single derivative of multiple functions is rather common (vectorization occurs over the vectors), we accelerate the algorithm further by considering multiple derivatives with corresponding
matrices with identical adjacency graphs. We specialize to four matrices and four derivatives, with 16 outputs, 
computed as a sum of outer products.

>>>>

Each core in the architecture has a 32kB L1 data cache, a 32kB L1
instruction cache, and a 512kB L2 cache. The architecture of a core is
based the traditional Pentium architecture which have been extended to
64-bit. A core can hold 4 hardware contexts at any time. And at each
clock cycle, instructions from a single thread are executed. Due to
some hardware constraints, two hardware contexts must be used to reach
the peak instruction throughput in that architecture. As in the
Pentium architecture, a core has two different concurrent instruction
pipelines which allow the execution of two instructions per
cycle. However, only one vector or floating point instruction can be
executed at each cycle.

@@

@@

\section{Conclusion}
\label{sec:ccl}

In the previous sections, we have explored in the practical
implementation on a MIC architecture of multiple derivative operators
acting on multiple vectors within the context of RBF-RD. Each
derivative has an associated sparse matrix with a fixed number of
non-zeros on each row. While computing a single derivative of multiple
functions is rather common (vectorization occurs over the vectors), we
accelerate the algorithm further by considering multiple derivatives
with corresponding matrices with identical adjacency graphs. We
specialize to four matrices and four derivatives, with 16 outputs,
computed as a sum of outer products.
